Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
fix typo
Assertion -> Expectation

    On might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
    {\tt Alternative} should satisfy the monoid laws\ldots'')
\end{quote}

@@

We propose four combinators, that can be used to set expectations
about the outcome of code examples.

A common expectation is, that a value should be equal to an other
value.

@@

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Assertion
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldSatisfy :: Show a => a -> (a -> Bool)
  -> Assertion
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldReturn :: (Show a, Eq a) => IO a -> a
  -> Assertion
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldThrow :: Exception e => IO a -> (e -> Bool)
  -> Assertion
\end{verbatim}\end{quote}

>>>>

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
    {\tt Alternative} should satisfy the monoid laws\ldots'')
\end{quote}

@@

We propose several combinators, that can be used to set expectations
about the outcome of code examples.  And we build them on top of
HUnit.

\begin{quote}\small\begin{verbatim}
type Expectation = Assertion
\end{verbatim}\end{quote}

\noindent A common expectation is, that a value should be equal to an other
value.

@@

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldSatisfy :: Show a => a -> (a -> Bool)
  -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldReturn :: (Show a, Eq a) => IO a -> a
  -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldThrow :: Exception e => IO a -> (e -> Bool)
  -> Expectation
\end{verbatim}\end{quote}
